Neural models for computer-assisted musical orchestration: a preliminary study

### 2020-05-09 paper/latex/paper.tex
Add info about TinySOL

\section{Data generation}
We used the TinySOL database to create our input data. \textbf{(Should we talk more about TinySOL here?)}

>>>>

\section{Data generation}
We used the TinySOL database to create our input data. TinySOL is a subset of the Studio On Line (SOL) database created by IRCAM. TinySOL contains 2,478 samples from 12 instruments. The instruments come from different orchestral families: strings, woodwinds, and brass are all represented in TinySOL. Each TinySOL sample is one instrument playing one note in the "ordinary" playing style.
